Assessing Replenishing Population

### 2023-12-11 minos/validation/replenishing.Rmd
Small path changes to existing scripts, and added a notebook for investigating interventions

Source utils for some functions.
```{r}
source('R_Scripts/utils.r')
```

```{r}
# Replenishing data
repl <- read.csv('Minos/data/replenishing/replenishing_pop_2019-2070.csv')

# scotland replenishing
#scot.repl <- read.csv('Minos/data/replenishing/scotland/replenishing_pop_2019-2070.csv')
```

>>>>

Source utils for some functions.
```{r}
source('Minos/minos/validation/utils.r')
```

```{r}
# Replenishing data
repl <- read.csv('Minos/data/replenishing/replenishing_pop_2015-2070.csv')

# scotland replenishing
#scot.repl <- read.csv('Minos/data/replenishing/scotland/replenishing_pop_2015-2070.csv')
```
